Prestige as a Driving Force in Cultural Transmission

### 2022-04-04 ms/PrestigeBias.tex
update

We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}. 
Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.

@@

\subsection*{Dichotomous trait}
To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
\begin{equation}\label{eq:binary-model}
P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} % TODO should it be G_{i,A} rather than P_i,A ?
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the indicator trait $\alpha'= \frac{\alpha}{1-\alpha}$.

@@

Examining variable values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
For high $\alpha$ values (above 0.5), very few simulations were needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$).
For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required. % TODO did you test other distributions?
% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?

Next, we examined the fixation probability and fixation time of an advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions.
First, we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$). 
%In the dichotomous model the estimation error will be added by using heterogeneous $J$ parameter, which controls the strength of the bias of \cref{eq:success_bias}. % TODO do we need this sentence?
When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
Even when the standard deviation is $0.1$, the fixation probability and time is similar~(\cref{fig:hetro_error}). 
We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$). We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(X,X)$. % TODO replace X and X with relevant symbols
We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\cref{fig:hetro_alpha}).

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{
  \textbf{Number of simulations needed to get a good approximation.}
  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations. % 1000 simulations of the model or of DM ??
  Markers for average value across simulations, error bars for 95\% confidence interval.
  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
  % TODO
  % remove legend
  % change y labels: "Fixation probability" "Fixation time"
  % change x label: "Number of simulations"
  % Kimura - black solid line
  % I removed J as you give beta(A) below, ok
  % it is not clear what "number of simulations needed" means.
  % what does "good enough" mean?
  % maybe y axis should be in relative error?
  % you should point to the equation for kimura.
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
  \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   High success weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it). Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
	% TODO
	% see comments in previous figure
\end{figure}

@@

After finding that the DM distribution is a good approximation of the (within-generations) role-model choice process, we turn our attention to the (between-generations) evolutionary dynamics.
We focus on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models. % References: 
% Kimura, M. On the probability of fixation of mutant genes in a population. Genetics 47, 713–9 (1962).
% Kimura, M. & Ohta, T. The Average Number of Generations until Fixation of a Mutant Gene in a Finite Population. Genetics 61, 763–71 (1969).
% Otto, S. P. & Whitlock, M. C. Fixation Probabilities and Times. in eLS (John Wiley & Sons, Ltd, 2013). doi:10.1002/9780470015902.a0005464.pub3.
We are mainly interested in the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias.
For simplicity, we do not include estimation error in this analysis.
As shown above, transmission in our model is approximately DM distributed with a parameters % TODO fill here from corollary 3 and eq 19, right?
% $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$. % what's \vec{V} here?

@@

In our model, $\alpha'$ is the odds ratio of a parameter we called "indicator weight", denoted in our model as $\alpha$, so:
\begin{equation}\label{eq:success_ratio}
\alpha' = \frac{\alpha}{1-\alpha}
\end{equation}

@@

\begin{figure}[h]
  \begin{center}
    %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
  \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
     \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size.
  Error bars show mean and 95\% confidence intervals.
  Effective population, $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point; Population size, $N=1,000$; $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
  \label{fig:var_alpha}
  % TODO
  % - better x and y label, as noted above
  % - in legend, replace "kimura" with "Approx."
  % - in legend, remove "=2s"
  % - change approximation color, it is too similar to WF simulations
  % - make the horizontal line black?
  % - caption should start with bold sentence summarizing the figure. 
  % - in caption add description of each parameter (as I did for N)
  %
\end{figure}

\begin{figure}[h]
  %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  % TODO 
  % - see previous figure
  % - consider making the error bars smaller with more simulations or narrower CI (50%?)
  % - consider using plt.xscale('log')
  % - maybe you can merge this figure with the figure?
  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
  \label{fig:var_beta}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
  %TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
  \begin{subfigure}{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients. Changing the effective population size doesn't affect the approximation, and it is condensed the mathematical expected values across all values. High values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values. Very high values ($s>0.35$) will even deviate from the constant environment expected values. This is expected because Kimura's approximation are only viable for low selection coefficient values.
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success weight is: $\alpha=0.1$. 
  }
  % TODO 
  % see previous figures..
  % not sure you need the green curve in the left panel
  % the right panel might be better with yscale('log')? or xscale('log')? right now it is hard to see that the blue even changes...
  % 
  \label{fig:ch_env_alpha_beta}
\end{figure}

We validate our results using simulations.
We find that $\alpha$ does not have a significant effect on the approximations (\cref{fig:ch_env_alpha_beta}).
However, $\beta$ does. 
We plotted along the modified estimation the original Kimura's estimation, as a limiter. % TODO rephrase, this sentence is not clear at all
We suspect that when $\beta$ is too large, there won't be many cycles in the simulations. This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or it get extinct very quickly, % TODO what gets extinct? what does "it" refers to?
 because the advantage it had in the $k$ generations wasn't sufficient, and the same $s$ becomes a greater disadvantage when the environment changes, resulting in fast extinction. % TODO read and rephrase.
For lower % TODO this was "higher" but should be "lower" right?
values of $\beta$ we see a deviation from the original estimation environment, % TODO what is "estimation environment"?
but it's to be expected, because Kimura's equations weak fitness (i.e., low selection coefficients, $s$).

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  %TODO add panel labels (a) and (b) on figures corner.
  % see previous figures todos
  % move legend to upper left? it is currently hiding something
  \caption{Model simulations compared with both the constant environment and the changing environment equations for different compositions of the environment cycle. % TODO reminder what k and l are.
   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
  \label{fig:ch_env_k_l}
\end{figure}

We also examined the effect of different choices of $k$ and $l$ while keeping a constant total cycle length, $n=k+l=40$.
We found that larger $k$-to-$l$ ratio increases the agreement between the modified equation and the original estimation of the constant environment. % "modified....environment" unclear.
When using higher values of $n$, the agreement between the approximation and simulation results is weaker.
This is because our approximation is more precise when more cycles occur.
When $n$ is high, there will be less cycles, % TODO why higher n gives less cycles?
and the simulations will get closer to the constant environment equation.

% TODO I think you can do a better job summarizing the results - does the approximation work? when doesn't it work? why?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
\paragraph{Summary.}
During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
Some cultural traits or cultural role-models may be more likely to be copied due to transmission biases. 
A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be correctly identified.
However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful by some other indicator.

Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias, which included both success and influence biases, where the latter is a bias towards role-models with many copiers. We found approximations for the role-model choice process: the generalized binomial distribution that approximates the number of copiers of a single role-model, and the Dirichlet-Multinomial distribution that approximates the distribution of copiers in the entire population in a \textit{rich-getting-richer} type of process. 
We then studied the effects of prestige bias on the fixation probability and time of an invading advantageous cultural phenotype in both a constant and a changing environment.
% TODO what did we find?

@@

According to \citet{animal_leadership}, there are two main approaches to group decision-making in nature: leadership and consensus.
Leaders may lead the group when traveling, decide on a nesting site, or choose foraging patches. They found that leadership is mostly observed when there is a profound social network in the group, % TODO profound sounds weird here. what do you mean by it?
and when there are individuals that present leadership behavior.
Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
When no individual posseses such traits, or when the social network is lacking, % TODO lacking what?
decisions are more likely to be made by consensus.
Leader may carry selection costs, e.g. due to higher predation risk, poisoning when exploring new foraging patches.
In some cases, %e.g. fish, % TODO ref for fish? otherwise don't mention fish
 the leader may be the hungriest or the weakest individual, while the others would prefer to follow the leader and minimizing their risks and costs.
However, leadership may also carry selection benefits. For example, given the route to the foraging site was successful, the leader and his closest followers would gain most or the best of the food, whereas in consensus decision making, the food would be shared more equally. Or, sexual selection may also provide a selection benefit advantage to leaders, who might gain more sexual partners due to their leadership of the group. \citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
They show that leaders wouldn't be chosen due to their superior abilities, but because they have the least to lose. % TODO are you sure? this is in baboons?

In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. However, wrong decision making that harms the group could result in harm.
In modern society it is less common to worry about mere survival, and so the prestigious positions, even though they are not without risks and costs, are not as dangerous as for animals in nature. % TODO reference? I'm not sure this is correct
This may be the reason humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them. % you give two reasons - "this may be the reason" and "as they may reap..." I think the latter is more correct. also I think it is personality and family driven, to an extent.
This is in complete contrast to animals, where the weakest/hungriest is driven to lead, compared to humans where leadership positions are mostly competitive. % TODO I'm not sure, let's discuss!

\citet{dual_leadership} suggest a different view of leadership. They note that most discussions assume there is one type of leadership, as seen above, and so they differ in their definitions. \citet{dual_leadership} suggest a way to solve said contradiction by defining two types of leaderships: prestige-based and dominance-based.
They present classical views of leaderships by Confucius and Machiavelli. Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills,
and (outstanding) personal qualities. This description is very similar to success bias in our model. % TODO I changed the end of the sentence, is it ok?
By contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence.
They say that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view into the complex and dynamic processes of leadership. 
Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style. This would require assuming some costs and benefits so that prestige has higher  rewards but greater costs, while dominance has lower rewards and lower costs. % TODO why?
The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.

% YOAV Here
\citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige based and dominance based leadership types.
By their definition, the latter is defined by acquiring social status by using aggression, intimidation and violence. It is also more common than prestige in non humans. Their definition of prestige is somewhat synonymous with ours. According to their manuscript, prestige is composed both of estimation in the eyes of people (our indicator/success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information. Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions and results, is consistent with ours.

>>>>

We begin with a continuous trait model with indirect bias suggested by \citet{evolutionBook}, develop an extension with influence bias, and then develop a model with a dichotomous trait.
We implemented our stochastic models and approximations, performed statistical analyses, and produced figures using Python \citep{python} with NumPy \citep{numpy} and Matplotlib \citep{mathplotlib}.

Source code is available at \href{https://github.com/yoavram-lab/PrestigeBias}{https://github.com/yoavram-lab/PrestigeBias}.

@@

\subsection*{Dichotomous trait}
To allow for mathematical analysis of the model, we introduce a simplified version where the indicator trait only has two phenotypes: the optimal phenotype $\hat{A}$ and the sub-optimal phenotype $A$. 
All role-models with the same phenotype will contribute to the probability of that phenotype to be transmitted, and thus influence is determined by the number of copiers that have already chosen a role-model with either phenotype.
Therefore, the probability of the $i$-th copier to copy phenotype $A$ is
\begin{equation}\label{eq:binary-model}
P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_{i,A}}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X} % TODO should it be G_{i,A} rather than P_i,A ?
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_{i,A}$ is the number of copiers that already chose $A$ when copier $i$ chooses a role-model and $\alpha'$ is the odd ratio of the bias weight $\alpha'= \frac{\alpha}{1-\alpha}$.

@@

Examining variable values of the bias weight parameter $\alpha$, the test p-value was always 1, meaning that the null hypothesis cannot be rejected.
For high $\alpha$ values (above 0.5), very few simulations are needed to reach p-value of 1 (less than five simulations for $\alpha=0.9$, and less than 20 for $\alpha=0.7$)
For very low $\alpha$ values, which means very high influence weight, the number of simulations needed was 100.
When testing our observed distributions against different distributions, for example the uniform distribution (all role-models have exactly one copier), the p-value was 0, so that the null hypothesis was rejected, as required.
% TODO did you test other distributions?
% ANS - No, mainly because I didn't know what paremeters to choose, we should discuss

% TODO figure of observed vs expected distribution, and maybe also for other distributions such as uniform
% ANS - observed vs expected of what? Make a histogram of number of copiers per role-model? just the top role-models?

% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?

Next, we examined the fixation probability and fixation time of an advantageous phenotype $\hat{A}$ when invading a population of phenotype $A$ and compared results from the full model and the DM approximation.
We find that the number of simulations needed to sufficiently approximate our model with the DM approximation is roughly $1,000$ (\Cref{fig:num_sims}).
Next, we examined the robustness of the DM approximation to relaxing the approximation assumptions.
First, we relaxed our assumption of no estimation error $e$.
Estimation error in the original model was drawn from a normal distribution, and added to the trait value before evaluation of the bias ($A_{ij} = A_j + e_i$).
When estimation error is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
Even when the standard deviation is $0.1$, the fixation probability and time is similar~(\cref{fig:hetro_error}). 
We also relaxed our assumption of a uniform bias weight $\alpha$ (i.e., $\alpha_i=\alpha$). We allowed $\alpha$ to vary in the population, drawing $\alpha_j$ for each role-model $j$ from a normal distribution such that $\alpha_j \sim N(X,X)$. % TODO replace X and X with relevant symbols
We found again that results of the DM approximation are similar to those from stochastic simulations of the full model~(\cref{fig:hetro_alpha}).

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{
  \textbf{Number of simulations needed to get a good approximation.}
  The approximation (orange) fits simulation results (blue) well when using 1,000 simulations for both models. 
  Markers for average value across simulations, error bars for 95\% confidence interval.
  Here, population size, $N=1000$; bias weight, $\alpha=0.5$; phenotype values, $\hat{A}=1$, $A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
  % TODO
  % Kimura - black solid line
  % I removed J as you give beta(A) below, ok
  % it is not clear what "number of simulations needed" means.
  % what does "good enough" mean?
  % maybe y axis should be in relative error?
  % you should point to the equation for kimura.
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   High bias weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it). Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
	% TODO
	% see comments in previous figure
\end{figure}

@@

After finding that the DM distribution is a good approximation of the (within-generations) role-model choice process, we turn our attention to the (between-generations) evolutionary dynamics.
We focus on the fixation probability and fixation time of an advantageous phenotype, similar to analyses in population-genetic models \citep{kimura,kimura_average,otto_fixation}.

We are mainly interested in the effect of the bias weight ($\alpha$), which determines the relative effects of success and influence on prestige bias.
For simplicity, we do not include estimation error in this analysis.
As shown above, transmission in our model is approximately DM distributed with the parameters $\sim DM(\alpha'X,(N-X)\alpha'\beta(A))$ based on \cref{cor:dirichlet} and \cref{eq:copier_choose}.

@@

In our model, $\alpha'$ is the odds ratio of a parameter we called "bias weight", denoted in our model as $\alpha$, so:
\begin{equation}\label{eq:success_ratio}
\alpha' = \frac{\alpha}{1-\alpha}
\end{equation}

@@

\begin{figure}[h]
%TODO remove the (a) and (b) from the latex and put them on the figure itself (top left corenr).
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
     \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size.
  Error bars show mean and 95\% confidence intervals.
  Effective population, $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point; Population size, $N=1,000$; $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
  % TODO
  % - better x and y label, as noted above
  % - in legend, replace "kimura" with "Approx."
  % - in legend, remove "=2s"
  % - change approximation color, it is too similar to WF simulations
  % - make the horizontal line black?
  % - caption should start with bold sentence summarizing the figure. 
  % - in caption add description of each parameter (as I did for N)
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[h]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  % TODO 
  % - see previous figure
  % - consider making the error bars smaller with more simulations or narrower CI (50%?)
  % - consider using plt.xscale('log')
  % - maybe you can merge this figure with the figure?
  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
  \label{fig:var_beta}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  %TODO remove the (a) and (b) from the latex and put them on the figure 	itself (top left corenr).
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients. Changing the effective population size doesn't affect the approximation, and it is condensed the mathematical expected values across all values. High values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values. Very high values ($s>0.35$) will even deviate from the constant environment expected values. This is expected because Kimura's approximation are only viable for low selection coefficient values.
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} bias weight is: $\alpha=0.1$. 
  }
   %TODO 
  % see previous figures..
  % not sure you need the green curve in the left panel
  % ANS - to show it's not a valid option to use?
  % the right panel might be better with yscale('log')? or xscale('log')? right now it is hard to see that the blue even changes...
  \label{fig:ch_env_alpha_beta}
\end{figure}

We validate our results using simulations.
We find that $\alpha$ does not have a significant effect on the approximations (\cref{fig:ch_env_alpha_beta}).
However, $\beta$ does.

We suspect that when $\beta$ is too large, there won't be many cycles in the simulations. This might happen if either the population reaches a high frequency of the fitter phenotype after only a few cycles, or the fitter phenotype get extinct very quickly. 
For the very high $\beta$ values (0.35 and above), the fixation probability exceeds even the constant environment approximation (which is the upper limit), but it's to be expected, because Kimura's equations are only appropriate for weak fitness (i.e., low selection coefficients, $s$).

\begin{figure}[h]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  %TODO add panel labels (a) and (b) on figures corner.
  % see previous figures todos
  % move legend to upper left? it is currently hiding something
  \caption{Model simulations compared with both the constant environment and the changing environment equations for different values of $k,l$, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
 We ran $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
  \label{fig:ch_env_k_l}
\end{figure}

We also examined the effect of different choices of $k$ and $l$ while keeping a constant total cycle length, $n=k+l=40$.
We found that larger $k$-to-$l$ ratio increases the agreement between the changing environment equation and the original estimation of the constant environment. 
When using higher values of $n$, the agreement between the approximation and simulation results is weaker.
This is because our approximation is more precise when more cycles occur.
When $n$ is high, the cycles are longer. When the cycles are long, the settings are similar to a constant environment equation, and fixation/extinction is more likely to happen. This means there will be less cycles, which lowers our approximation accuracy.

\section*{Discussion}
\paragraph{Summary.}
During cultural transmission, cultural traits such as attitudes, values, beliefs, and behavioral patterns are transmitted between individuals, for example via copying and social learning.
Some cultural traits or cultural role-models may be more likely to be copied due to transmission biases. 
A common one is success bias, in which copiers are more likely to copy a successful role-model. Many models assume that success can be correctly identified.
However, it has been suggested \citep{complexityPaper} that because estimating success is hard, a more common bias is \textit{prestige bias}---a bias towards role-models perceived to be successful by some other indicator.

Inspired by a model by \citet{evolutionBook}, we developed a cultural-evolution model with prestige bias, which included both success and influence biases, where the latter is a bias towards role-models with many copiers. We found approximations for the role-model choice process: the generalized binomial distribution that approximates the number of copiers of a single role-model, and the Dirichlet-Multinomial distribution that approximates the distribution of copiers in the entire population in a \textit{rich-getting-richer} type of process. 
We then studied the effects of prestige bias on the fixation probability and time of an invading advantageous cultural phenotype in both a constant and a changing environment.
% TODO what did we find?
% TODO I think you can do a better job summarizing the results - does the approximation work? when doesn't it work? why?

@@

According to \citet{animal_leadership}, there are two main approaches to group decision-making in nature: leadership and consensus.
Leaders may lead the group when traveling, decide on a nesting site, or choose foraging patches. They found that leadership is mostly observed when there are a lot of connections in the social network of the group, and when there are individuals that present leadership behavior.
Leaders would usually be high-ranking members of the group: elders, individuals with many kin relations, or individuals possessing other dominant traits.
When no individual posseses such traits, or when there are not enough connections and relations in the social network, decisions are more likely to be made by consensus.
Leaders may carry selection costs, e.g. due to higher predation risk, poisoning when exploring new foraging patches.
In some cases, the leader may be the hungriest or the weakest individual, while the others would prefer to follow the leader and minimizing their risks and costs.
However, leadership may also carry selection benefits. For example, given the route to the foraging site was successful, the leader and his closest followers would gain most or the best of the food, whereas in consensus decision making, the food would be shared more equally. Or, sexual selection may also provide a selection benefit advantage to leaders, who might gain more sexual partners due to their leadership of the group. \citet{animal_leadership} describe benefits for the closest associates of a dominant baboon, such as protection from predators. 
In some species, like the females of \textit{Eulemur fulvus rufus} (Red lemur), leaders may arise due to nutritional needs, and not due to possessing superior traits \citep{lemurs}.

In humans, leadership also has its costs and benefits. Leaders can make decisions that would most benefit them and their closest followers, while still maintaining group cohesion. However, wrong decision making that harms the group could result in harm.

In modern society humans strive for the prestigious positions, as they may reap rewards greater than the risk and costs to achieve them, or due to individual personality and pressure/education from the family.

\citet{dual_leadership} suggest a different view of leadership. They note that most discussions assume there is one type of leadership, as seen above, and so they differ in their definitions. \citet{dual_leadership} suggest a way to solve said contradiction by defining two types of leaderships: prestige-based and dominance-based.
They present classical views of leaderships by Confucius and Machiavelli. Confucius views leaders as role-models who exercise influence through possessing superior knowledge, skills,
and (outstanding) personal qualities. This description is very similar to success bias in our model. 
By contrast, Machiavelli views leaders as rulers who exercise influence by imposing costs through (the threat of) punishment and violence.
They say that these two opposing views are both partially supported by the available evidence but each one on its own offers an incomplete view into the complex and dynamic processes of leadership. 
Our model does not reflect these leadership styles, but several adjustments could be made in order to match it, such as assuming there is a correlation between phenotype to leadership style. 
The emerging cultural-evolutionary dynamics and their dependence on the costs and benefits are intriguing.

\citet{prestige_evolution} support said claim that there are two types of leadership, and also define the two as prestige based and dominance based leadership types.
By their definition, the latter is defined by acquiring social status by using aggression, intimidation and violence. It is also more common than prestige in non humans. Their definition of prestige is somewhat synonymous with ours. According to their manuscript, prestige is composed both of estimation in the eyes of people (our indicator/success trait) and commanding position in people's minds, i.e number of copiers people think they have, which they define as \textit{influence} (similar to our definition for influence).
In their paper, they show that prestige evolved from natural selection, as an efficient process to extract reproductive benefit from the flow of socially transmitted information. Simply put, prestige is a natural step where social learning exists, due to saving costs of individual learning.
It could be interesting in the future to expand our model using this idea: observing the copier trait of \textit{evaluation}, rather than only observing the evolution of the indicator trait copied.
\citet{prestige_evolution} suggest that the most skilled role-models will, on average, end up with most copiers. Their research, definitions and results, is consistent with ours.

So far we presented the theory behind prestige, and it's appearance in nature. The following will show the appearances of prestige biases in humans, and in recent times.
